% Copyright (c) 2014,2016 Casper Ti. Vector
% Public domain.

\chapter{攻读硕士学位期间的科研成果}
\begin{itemize}
\item \textbf{Chao Lv}, Lili Yao, Yansong Feng and Dongyan Zhao. Improving Collaborative Filtering with Long-Short Interest Model. NLPCC 2016.
\item \textbf{Chao Lv}, Yansong Feng and Dongyan Zhao. Purchase Prediction via Machine Learning in Mobile Commerce. NLPCC 2016.
\item \textbf{Chao Lv}, Runwei Qiang, Feifan Fan and Jianwu Yang. Knowledge-based Query Expansion in Real-Time Microblog Search. AIRS 2015.
\item \textbf{Chao Lv}, Runwei Qiang, Lili Yao and Jianwu Yang. EEST: Entity-driven Exploratory Search for Twitter. AIRS 2015.
\item \textbf{Chao Lv}, Feifan Fan, Runwei Qiang, Yue Fei and Jianwu Yang. PKUICST at TREC 2014 Microblog Track: Feature Extraction for Effective Microblog Search and Adaptive Clustering Algorithms for TTG. TREC 2014.
\item Yue Fei, \textbf{Chao Lv}, Yansong Feng and Dongyan Zhao. Real-time Filtering on Interest Profiles in Twitter Stream. JCDL 2016.
\item Lili Yao, \textbf{Chao Lv}, Feifan Fan, Jianwu Yang, Dongyan Zhao PKUICST at TREC 2016 Real-Time Summarization Track: Push Notifications and Email Digest. TREC 2016.
\item Feifan Fan, Yue Fei, \textbf{Chao Lv}, Lili Yao, Jianwu Yang and Dongyan Zhao. PKUICST at TREC 2015 Microblog Track: Query-biased Adaptive Filtering in Real-time Microblog Stream. TREC 2015.
\item Feifan Fan, Runwei Qiang, \textbf{Chao Lv} and Jianwu Yang. Improving Microblog Retrieval with Feedback Entity Model. CIKM 2015.
\item Feifan Fan, Runwei Qiang, \textbf{Chao Lv}, Wayne Xin Zhao and Jianwu Yang. Tweet Timeline Generation via Graph-based Dynamic Greedy Clustering. AIRS 2015.
\item \textbf{吕超}，强闰伟，姚丽丽，杨建武，``一种基于多来源实体驱动的探索性微博检索系统''，专利号：201510246802.5
\end{itemize}
